Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy

### 2024-09-06 index.qmd
create gh-pages for NEST

---
title: Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy
author: Philipp Jonas Kreutzer
date: last-modified
bibliography: swinno-shades-green.bib
csl: 'https://zotero.org/styles/apa?source=1'
format: 
    pjk_theme-revealjs
---

>>>>

---
title: Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy
author: Philipp Jonas Kreutzer
date: last-modified
bibliography: swinno-shades-green.bib
csl: 'https://zotero.org/styles/apa?source=1'
format: 
    pjk_theme-revealjs:
        embedd-resources: true
---
